### 2016-09-29 results.tex
gbf

\todo{Insert correctness theorem for \emph{private}~$M$ in the ROM.}
\begin{theorem}
Fix $k,m,n,r,\lambda>0$, a set~$\elts$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the garbled Bloom filter (set membership) data structure over~$\elts$. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  [...]
\]
\end{theorem}

>>>>

Switching now to the case of a \emph{private}~$M$ GBF, we have the following correctness bound.
\todo{Insert correctness theorem for \emph{private}~$M$ in the ROM.}
\begin{theorem}
Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private~$M$ GBF. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  [...]
\]
\end{theorem}
